Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction.tex
Cosmetic changes.

In this section, we reconstruct each \Metis inference rule
in Table~\ref{tab:agda-metis-table} with a
function and its respective theorem. We present a pattern of the
formal description for these rules.

\begin{notation}

The function name written in \texttt{typewriter} font refers to a \Metis
inference rule. The same function name written using \textsf{sans serif} font
refers to our proposed version to reconstruct the rule and implemented
in~\cite{AgdaMetis}. We use \Source and \Target as synonyms of \Prop type to
describe in the function type the role of the arguments.

\end{notation}

\begin{myexamplenum}
\Metis has a inference rule named conjunct.
We refer to this rule writing \conjunct.

\begin{verbatim}
  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
\end{verbatim}

The pattern of the formalization for this rule is the following. For the
\conjunct rule, we define in type theory a function using the same name,
\fconjunct, but written using \textsf{san serif} font to distinguish from the
original. The \fconjunct function has the following pattern:

 \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fconjunct : \Source → \Target → \Prop\\
  &\begin{array}{ll}
  \fconjunct~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
         &\text{transformations or other rules to }φ;\\
      φ, &\text{otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}

\begin{itemize}
  \item[∙] $φ : \Source$ is the \emph{source} formula from a previous deducted derivation.
  \item[∙] $ψ : \Target$ is the \emph{target} formula. The expected result of the \fconjunct rule.
\end{itemize}

To justify all transformations done by the \fconjunct rule, we prove its
soundness with a theorem. This theorem would be

\begin{equation*}
\text{If }Γ ⊢ φ\text{ and }ψ : \Target \text{ then }Γ ⊢ \fconjunct~φ~ψ.
\end{equation*}

\end{myexamplenum}

>>>>

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table} via a function and its respective
theorem. We present a pattern of the formal description for these
rules in Example~\ref{ex:inference-rule-pattern}.

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule. The same function name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and implemented in~\cite{AgdaMetis}. We use
  \Source and \Target as synonyms of the \Prop type to describe in the
  function types the role of the arguments.
\end{notation}

\begin{myexamplenum}
\label{ex:inference-rule-pattern}
\Metis has a inference rule named \conjunct. We reconstruct this
inference rule as follow. We define in \Agda the function
\fconjunct which has the following pattern:
\begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fconjunct : \Source → \Target → \Prop\\
  &\begin{array}{ll}
  \fconjunct~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
         &\text{transformations or other rules to }φ;\\
      φ, &\text{otherwise;}
      \end{cases}
  \end{array}
  \end{aligned}
\end{equation*}

To justify all transformations done by the \fconjunct rule, we prove
its soundness with a theorem. This theorem would be
\begin{equation*}
  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fconjunct~φ~ψ, \text{ where } ψ : \Target.
\end{equation*}
\end{myexamplenum}
